---
title: "linear model from Web"
author: "JovyGomez"
date: "Fall 2024" 

output:
   html_document:
         toc: true
         toc_depth: 5
        
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Read about the data from the website where it is staged.  Then form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 

 


```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(rgl)
require(knitr)

```

```{r}
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  

```

## Model 1 SIM~ARMS

### scatterplot

```{r}
plot(SIMS~ARM,data=data)
model1=lm(SIMS~ARM, data=data)
abline(model1)
```

This scatter plots shows Stimulated increased as ARM strength increase


         
### Numerical results

```{r}
cor(SIMS~ARM,data=data)
```

Correlation= 0.69 shows moderate positive correlation beetween SIMS score and ARM Strength
          
### Inferential  (Build model.1)

```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```

Model.1 shows that the intercept -4.095 and coefficient 0.055 of ARM are both of these are significantly different from zero. 

#### Predict at target point

```{r}
targtPoint = data.frame(GRIP=94, ARM=88)
predictInt= predict(model.1, targtPoint, interval = 'prediction') 
print(predictInt)
               
```
#### scatterplot with model fit
at ARM=88, GRIP=94 the predicted SIMS score is 0.71. At that score the 95% confidence interval for that score is SIMS between -1.73 and 3.14

## Model 2 SIM~GRIP
```{r}
plot(SIMS~GRIP,data=data)
model.2=lm(SIMS~GRIP, data=data)
abline(model.2)
```
The scatter plot shows that simulated strengthb score increases depending on the amount of the GRIP strength exerted by an individual.  

### Numerical Results

```{r}
cor(SIMS~GRIP,data=data)
```


The numerical results show that the correlation equals 0.64 shows that there is a moderate positive correlation between simulated strength scores and ARM strength  

### Infrential Results

```{r}
model.2 <- lm(SIMS~GRIP,data=data)
summary.lm(model.2)
```

The model shows that the intercept -4.809 and coefficient 0.045 GRIP are both significantly different from zero

### predict model.2 at target point 
```{r}
targtPoint = data.frame(GRIP=94, ARM=88)
predictInt= predict(model.2, targtPoint, interval = 'prediction') 
print(predictInt)
               
```
At ARM=88, GRIP=94, the predicted SIMS score is -0.54. At that score the 95% confident interval shows that the score of SIMS is between -3.11 and 2.04 
### now add the model fit to our plot for model.2 


## Model 3 SIM~ARM=GRIP
```{r}
model.3 = lm(SIMS~ARM+GRIP,data=data)
summary(model.3)
```

Model.3 shows that intercept -5.434, coefficient 0.038 of ARM, and coefficient of GRIP is 0.025 and they are all significantly different from zero 
### Numerical results (cor)
```{r}
cor(data)
```
Sims correlates with GRIP and ARM with these values 


### predict model.3 at target point 
```{r}
predict(model.3, targtPoint,interval='prediction')
```

At ARM=88  GRIP=94 The predicted SIMS sore is 0.15. 95% confidence interval for that score is SIMS between -2.14 and 2.44


## comparing nested models ANOVA Test 


### Model.1 vs Model.3 
### Model.2 vs Model.3 

## Informally compare Model.1 with model.2 
```{r}
anova_result <-anova(model.1,model.3)
print(anova_result)
```

The P value of the comparison of model.1 and model.3 is 0.000004994 which is less than 0.05, this means that the models are diffrent and model.3 is better. 
```{r}
anova_result <-anova(model.2,model.3)
print(anova_result)
```

The P value of the comparison of model.2 and model.3 is 0.000000001495 which is less than 0.05, this means that the models are different and model.3 is better 
